\section{Experimental Protocol}
\label{sec:experiments}

\subsection{Synthetic Development and Structural Ablation}
The development study uses six processes and five seeds per process, for 30 complete trajectories. Each trajectory retains 2,000 observations after a burn-in of 500 and is split chronologically 20/45/15/20 into prior, bound, validation, and test roles. Table~\ref{tab:synthetic_processes} gives the data-generating definitions; complete initialization and parameter details are provided in the supplementary material and configuration files.

\input{tables/synthetic_processes}

The original structural ablation compares ridge, fixed-$K$ all-active TSK with $K=12$, radius-controlled all-active TSK, and radius-controlled Top-3 TSK. Candidate lags are $\{3,5,10,15,20\}$, ridge penalties are $\{10^{-4},10^{-3},10^{-2},10^{-1},1\}$, and radii are $\{0.5,0.75,1,1.25,1.5,1.75,2,2.5,3,4,5\}$. The rule cap is 12. The certificate uses temperatures $\{0.125,0.25,0.5,1,2,4\}$, the prior scales and posterior ratios in Section~\ref{sec:certificate}, and familywise confidence $\delta=0.05/30$.

Candidate rows contain no test metric. For each family and selection strategy, the selected candidate is serialized before the synthetic test role is opened. The original four-family engine evaluated 12,700 eligible candidates with no build failures.

\subsection{Exploratory Fixed-$K$ Sensitivity and Statistical Inference}
To avoid interpreting the $K=12$ contrast as evidence for radius construction itself, an explicitly exploratory extension evaluates fixed $K\in\{2,3,4,6,8,12\}$. The lag, ridge, radius, posterior, loss, confidence, and chronological protocols remain unchanged. Every fixed $K$ pays the same normalized geometric rule-count code as the radius-controlled family; selection of $K$ is therefore not free. The one-rule case is excluded from the primary fuzzy sensitivity analysis because it is an affine degeneracy. The extended engine evaluates 16,450 eligible candidates with no build failures.

Paired series-level differences use 20,000-resample bootstrap intervals and two-sided Wilcoxon signed-rank tests with Holm correction. Rank-biserial effect sizes are reported. For energy trajectories, uncertainty is assessed with moving-block bootstrap because forecast errors are serially dependent. PJM uses a primary 14-day block with 7- and 28-day sensitivity analyses; Tetouan uses a primary seven-day block at its two-hour resolution. These analyses quantify uncertainty for the observed trajectories and do not create a new confirmatory experiment.

\subsection{Tetouan Development Decision Case}
The first operational study uses the UCI Tetouan City power-consumption data \cite{uci_tetouan_849}. Ten-minute observations are aggregated to two-hour means for three zones and split 20/45/15/20. Candidate families are ridge, fixed eight-rule TSK, and radius-controlled TSK with lags $\{3,6,12\}$. The initial gate combines a certificate threshold, clipping control, and a validation comparison with a 12-step seasonal-naive fallback. Underforecast errors receive weight two and overforecast errors weight one. This study is developmental: its negative test outcome is retained and used only to redesign the later gate. Full gate logic and run metadata are moved to the supplementary material.

\subsection{Internally Locked PJM Holdout Case}
After the Tetouan outcome, a stricter gate was frozen before opening PJM test outcomes. Four predeclared regional hourly-load series---AEP, COMED, DAYTON, and PJME---are taken from the public Hourly Energy Consumption collection \cite{mulla_hourly_energy}. Duplicate timestamps are averaged, and the common interval from 1 January 2012 through 2 August 2018 is aggregated to 2,406 daily means per region, requiring at least 23 hourly values per retained day. No exogenous variables are used.

The split is 20/45/15/20. Candidate families are ridge, fixed eight-rule TSK, and radius-controlled TSK; lags are $\{7,14,28\}$ days, radii are $\{0.75,1,1.25,1.5,2,2.5\}$, and ridge penalties are unchanged. Confidence is $0.05/4$. Eligibility combines an untruncated certificate threshold of 0.10, certification clipping no larger than 2\%, validation improvements of at least 5\% over seven-day seasonal naive in both RMSE and asymmetric cost, and blockwise temporal-stability constraints. Among eligible candidates, validation asymmetric cost is primary. If none qualifies, the fallback is deployed.

All four decisions are serialized and hashed before test forecasts are computed. The gate, candidate family, and decisions are unchanged in all subsequent analyses. A compute-only interruption occurred before test opening and was recovered with unchanged locked inputs; the incident chronology, hashes, and restart evidence are reported only in the supplementary audit rather than in the main narrative.

\subsection{Secondary Post-Hoc SARIMA and ETS Benchmarks}
After the original PJM outcomes were opened, we added simple statistical forecasting comparisons to contextualize the seven-day seasonal-naive baseline. The analysis is explicitly secondary and post hoc: it does not modify the gate, certificates, pretest decisions, or confirmatory interpretation. For each PJM region, a finite SARIMA grid and a finite exponential-smoothing (ETS) grid are selected using the original validation segment and asymmetric-cost criterion. The selected specification is then fitted on all pretest observations and evaluated by rolling one-step forecasts with fixed parameters and observed-target state updates. Test outcomes are not used for hyperparameter selection. Full candidate grids and per-region results are given in the supplementary material and reproducibility artifact.

\subsection{Post-Hoc Fuzzy-Rule Inspection}
To show what the learned fuzzy structures actually represent, we reconstruct two selected multi-rule development models without changing their fits: a five-rule radius TSK for SETAR seed 3001 and the four-rule Tetouan zone-1 model. Antecedent centers and spreads are transformed back to original data units, posterior-center local consequents are expressed as affine functions of lagged observations, and mean firing weights are computed on bound plus validation observations. These are interpretability summaries of deterministic point models, not additional model selection and not direct PAC-Bayesian guarantees.

\subsection{Metrics and Interpretation}
Synthetic prediction is summarized by standardized RMSE and MAE. Energy studies report raw-scale RMSE, MAE, and asymmetric absolute cost. Certificate values, empirical Gibbs upper terms, structural cost, Gaussian KL, randomized dimension, rule count, and target/forecast clipping are recorded separately. The deterministic posterior-center predictor in \eqref{eq:point_predictor} produces the reported validation and test forecasts; the certificate directly concerns the Gibbs predictor and clipped BMA defined in Section~\ref{sec:model}. A certificate is therefore treated as a screening quantity and never as direct evidence that the point predictor beats a forecasting baseline.
