\section{Discussion and Limitations}
\label{sec:discussion}

\subsection{An Integration Result, Not a Model-Superiority Result}
The strongest contribution of the study is methodological integration. The framework places chronological prior construction, complete structural coding, Gaussian posterior localization, bounded sequential risk, model selection, and operational abstention inside one auditable pipeline. Each element is individually established or technically standard; the contribution lies in making their interaction explicit and reproducible for linear and TSK forecasters under temporal dependence.

The structural experiments support a precise but limited mechanism. Replacing an unnecessarily dense 12-rule TSK model with a smaller rule base reduces randomized dimension, Gaussian KL, and certificate value. The Fixed-$K$ sensitivity analysis shows, however, that small predeclared fixed rule bases can match or improve on radius control. The supported conclusion is therefore that removal of complete rule blocks matters for the charged complexity. The present evidence does not establish that radius construction is intrinsically superior to every alternative way of choosing a compact rule base.

Top-3 activation provides a complementary negative result. It changes the number of rules evaluated at a sample but leaves the randomized consequent dimension unchanged. Its negligible certificate effect is therefore consistent with the mathematical accounting. For certificate-aware fuzzy design, sparsity must operate on the parameterized rule structure or on a posterior over rule inclusion, not only on firing-strength truncation at prediction time.

\subsection{Interpretability and Its Boundary}
The reconstructed SETAR and Tetouan rules show that the implementation learns distinct local affine relationships associated with different antecedent prototypes. This is useful for auditing the model and checking that a multi-rule TSK system is not merely duplicating one global regression. It is not evidence that the prototypes correspond to physically validated regimes, and it is not evidence that interpretability guarantees robustness. The Tetouan multi-rule model is the clearest warning: its rules are inspectable, yet the deployment decision fails on the held-out horizon.

The operational point forecasts are deterministic posterior-center predictions, whereas the PAC-Bayesian guarantee directly covers the Gibbs predictor and, by convexity, the clipped Bayesian model average. Before clipping, the posterior mean of a linear-in-consequents TSK predictor equals the posterior-center prediction. After clipping, equality with the clipped BMA generally fails. The certificate is therefore used as a screening statistic rather than represented as a direct guarantee for the deployed point forecast.

\subsection{Operational Evidence and Stronger Baselines}
The negative Tetouan study and positive internally locked PJM holdout illustrate why a certificate alone is not a deployment rule. The redesigned PJM gate combines certificate thresholding with validation margins and blockwise temporal-stability checks. Moving-block-bootstrap intervals remain positive for the original PJM comparison with seasonal naive, but these intervals quantify uncertainty only for the observed trajectories and do not prove population-level transfer to other regions or future regimes.

The secondary SARIMA and ETS analysis materially narrows the operational interpretation. SARIMA improves on the originally deployed point forecast in all four PJM regions, while ETS is competitive and sometimes better. Because these comparisons were designed after the PJM outcomes were opened, they are post hoc and cannot replace the frozen protocol. They nevertheless show that the gain over seasonal naive is not specific to TSK or PAC-Bayesian selection. The defensible operational contribution is an auditable process for screening, margin checking, and abstention, not superior forecasting accuracy relative to established statistical methods.

\subsection{Limits of the Certificate}
The certificate controls average conditional risk of a clipped Gibbs predictor over the certification horizon and transfers to the clipped BMA. It does not control raw RMSE, the deterministic posterior-center predictor, an unseen future horizon, or relative performance against another forecasting method. Structural-break experiments demonstrate the practical cost of the bounded-loss construction: when a prior-fixed clipping interval is exceeded frequently, the certificate remains formally valid for the clipped loss but loses relevance to raw-scale errors.

Heavy-tail or variance-adaptive supermartingale bounds \cite{haddouche2023heavy,rodriguez2024more} are a principled next step, but they require a separately verified implementation. The time-uniform proposition is evaluated numerically only at the final certification horizon; the paper does not claim an executed confidence sequence over all prefixes.

\subsection{Remaining Empirical and Procedural Limitations}
The synthetic study uses five seeds per process. The paired analysis is adequate for large structural contrasts such as Radius TSK versus fixed $K=12$, but it is not sufficient to characterize all nonlinear regimes or small performance differences. The PJM case contains four regional series over one common historical interval and uses no exogenous variables. The post-hoc statistical grid is intentionally simple and does not cover gradient boosting, modern probabilistic forecasting, or deep sequence models.

The PJM protocol is internally locked and supported by hashes, manifests, and pretest decision files, but it was not externally preregistered. A compute-only interruption occurred before test opening; recovery used unchanged locked inputs. The complete chronology is retained in the supplementary audit. These controls improve traceability but are not equivalent to an external timestamped preregistration.

\subsection{Implications for Future Fuzzy-System Research}
A stronger fuzzy contribution would replace deterministic radius construction with a posterior over rule inclusion or a certificate-aware structural learning objective. Such a method could jointly trade predictive fit, interpretable rule blocks, and charged complexity. It should be compared fairly with small fixed-$K$ grids and with strong statistical and machine-learning baselines. Domain-expert validation of learned rule semantics would also be needed before presenting local prototypes as operational explanations rather than model diagnostics.
