\section{Conclusion}
\label{sec:conclusion}

This work presents an auditable framework that combines chronological prior construction, explicit structural coding, a computable sequential PAC-Bayesian certificate, linear and TSK forecasting families, and conservative deployment screening. The general supermartingale inequality is established in prior work; the contribution is its fully charged, reproducible specialization and the empirical separation of different kinds of sparsity.

The structural experiments show that removing complete TSK rule blocks can reduce randomized dimension, Gaussian KL, and certificate value relative to an unnecessarily dense rule base. The additional Fixed-$K$ sensitivity prevents a stronger claim: small fixed rule bases can match or tighten the radius-controlled certificate, so the evidence supports structural compactness rather than universal superiority of radius selection. Sparse activation alone does not deliver the same complexity reduction when all consequent coordinates remain randomized and charged.

The energy studies show that a valid certificate can contribute to a broader screening rule but cannot replace forecasting validation. The first Tetouan gate fails. The redesigned PJM gate succeeds relative to its predeclared seasonal-naive fallback, yet the selected models are linear or one-rule affine predictors. Secondary post-hoc SARIMA and ETS benchmarks often improve further on the deployed point forecasts. Accordingly, the real-data evidence supports transparent model screening, validation margins, temporal-stability checks, and abstention; it does not establish nonlinear fuzzy-model dominance or state-of-the-art forecasting accuracy.

The main conclusion is therefore modest: PAC-Bayesian complexity can be made explicit and auditable for linear and TSK time-series models, and true structural rule reduction can tighten that accounting. Future work should learn a posterior over rule inclusion, align the certified and operational prediction objects more directly, compare against stronger forecasting baselines in a new externally timestamped protocol, and replace clipping with verified heavy-tail or variance-adaptive sequential guarantees.


\section*{Data and Code Availability}

The source code, processed data, experimental configurations,
result tables, audit manifests, and supplementary materials
supporting this study are publicly available at
\url{https://github.com/muneeff/pacbayes-sparse-tsk}.

The exact version associated with this manuscript is archived as
release v4.3.1:
\url{https://github.com/muneeff/pacbayes-sparse-tsk/releases/tag/v4.3.1}.

Raw third-party datasets are not redistributed. Download,
verification, and preprocessing scripts are provided in the
repository.


\section*{CRediT Author Statement}
Muneef Abdulkareem Farea Ahmed: Conceptualization,
Methodology, Software, Validation, Formal analysis,
Investigation, Data curation, Visualization, Writing--original
draft, Writing--review and editing, and Project administration.

\section*{Funding}
This research did not receive any specific grant from funding
agencies in the public, commercial, or not-for-profit sectors.

\section*{Declaration of Competing Interest}
The author declares that he has no known competing financial
interests or personal relationships that could have appeared to
influence the work reported in this paper.